Eye-tracking on the web: lessons learned from replicating 5 experiments

### 2022-05-18 manuscript.Rmd
add information about statistical power

In order to have adequate statistical power and precision, we aimed for XXXX participants per experiment.

>>>>

In order to have adequate statistical power and precision, we aimed for 2.5x the
sample size of the original experiment, following the heuristic of Simonsohn @simonsohn215.
In study 5, the original sample size was so small that we opted to collect 5x the 
number of participants to increase precision. Because of budget and time constraints 
we were unable to  replace the data for subjects who were excluded or whose data was 
missing due to technical failures.
